A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-18 sanity/paper1.tex
Input the bib
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1100 43ef1190-90fd-4dd7-a769-d0121f02b80e
Final proofreading
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1101 43ef1190-90fd-4dd7-a769-d0121f02b80e

We also looked for other headers in \ref{tab:headers}. We found
\httph{Pragma} (archaic HTTP 1.0 header) in 287 responses, but except
for two hosts, where they were superfluous, they were only used to
prohibit caching. \httph{Surrogate-Capability} were not observed.

@@

For SPARQL endpoints, it is interesting to examine the queries in a
shared proxy, e.g. an institutional cache or a Content
Delivery Network for frequent subpatterns, and prefetch and cache such
intermediate results so that subsequent queries can be answered in
part by the proxy.

@@

Furthermore, by using similarity measures, like those discussed in
\cite{dividino2013following}, proxies can proactively prefetch data
into a cache to help answer queries. A cost model that takes into
account several data access methods, those described by
\cite{hogan2014paths} as well as  the novel work in \cite{ldf1} may be
a key ingredient in enabling efficient SPARQL evaluation on the Web.

@@

%\bibliographystyle{plain}
\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{egne,webarch,data,rfc,hypermedia,dynamicity,stat1,specs,vocabs,similarity,optimization}

>>>>

We also looked for other headers in Table~\ref{tab:headers}. We found
\httph{Pragma} (archaic HTTP 1.0 header) in 287 responses, but except
for two hosts, where they were superfluous, they were only used to
prohibit caching. \httph{Surrogate-Capability} were not observed.

@@

@@

Furthermore, by using similarity measures, like those discussed in
\cite{dividino2013following}, shared proxies, e.g. an institutional
cache or a Content Delivery Network, can examine queries for frequent
subpatterns and proactively prefetch data into a cache to help answer
queries on the proxy. A cost model that takes into account several
data access methods, those described by \cite{hogan2014paths} as well
as the novel work in \cite{ldf1} may be a key ingredient in enabling
efficient SPARQL evaluation on the Web.

@@

%\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
%\bibliography{egne,webarch,data,rfc,hypermedia,dynamicity,stat1,specs,vocabs,similarity,optimization}
\input{paper1.bbl}
